Re-run, Repeat, Reproduce, Re-use, Replicate:\\Transforming Code into Scientific Contributions

### 2017-06-29 main.tex
Update on Overleaf.

Since scientists have a tendency to base their work on results they can verify, a reproducible and re-usable code offers a platform both verified and easy-to-use, fostering the development of derivative work by other researchers. Those derivative works contribute to the impact of your original contribution, and generate citations.

@@

Making your program re-usable means it can be used by people outside your lab,
using possibly different environment, different parameters or different data.
If people start using your program, they will most likely report bugs or malfunctions they encountered while using your program.
If you're lucky enough, they will even propose you bugfixes, hence improving the overall quality and correctness of your software.
In other words, if your program is re-usable and is re-used, it is alive.
As such, and as for any other living being, it will evolve and mutate to adapt to its environment.
This process will ensure long-term reproducibility to the extent people continue using and maintaining the program.\\

>>>>

Moreover, scientists prefer to base their work on results they can verify. A reproducible and re-usable code offers a platform both verified and easy-to-use, fostering the development of derivative works by other researchers. Those derivative works contribute to the impact of your original contribution, and generate citations.\\

Having more people examining and using your code also means that potential errors have a higher chance to be caught. If people start using your program, they will most likely report bugs or malfunctions they encountered while using your program. If you're lucky enough, they might even propose you either bugfixes or improvements, hence improving the overall quality of your software. This process contributes to the long-term reproducibility to the extent people continue to use and maintain the program.

@@
